---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# evreg


## Extreme Value Regression

### What does evreg do?

The `evreg` package provides functions that model non-stationary extreme values using univariate extreme value regression modelling, while also performing variable selection to objectively determine the best model for a given dataset. This is achieved by using generalized linear modelling for each parameter, and by fitting models with maximum likelihood estimates.

### A simple example

One of the main functions in the evreg package is `gevreg`, which performs the model fitting for generalized extreme value regression modelling. Then, `forward_gevreg` can be used to perform forward selection to objectively determine the best model. 
The following code fits a GEV regression model using the `gevreg` function for `fremantle` dataset and then uses `forward_gevreg` perform forward selection.

```{r}
data <- fremantle[ , -which(names(fremantle) %in% c("Year"))]
fit0 <- gevreg(SeaLevel, data)
forward_gevreg(fit0)
```



### Installation

To get the current released version from CRAN:

```{r installation, eval = FALSE}
install.packages("evreg")
```

### Vignette
